Scattering from compact objects: \\ Regge poles and the Complex Angular Momentum method

### 2019-12-06 rainbowCAM.tex
work on classification of QNM section

The $w$-modes (quasinormal modes) may be divided into three branches:
	\begin{enumerate}
   \item Curvature modes, oscillations whose damping is larger for less compact bodies. \sam{Anything else to say on curvature modes?}
   \item Interface modes ($\omega_{\text{II}}$-modes \cite{Leins:1993zz}), characterised by very rapid damping (i.e.~large negative imaginary part of $\omega_{\ell n}$). This branch of modes is most similar to the Schwarzschild black hole quasinormal modes. 
   \item Trapped modes \cite{Chandrasekhar449}: These modes exist for UCOs with $R/M < 3$, because the effective radial potential has a local minimum inside the star, and local maximum near the photon sphere $r=3M$. %The trapped modes are essentially the first few curvature modes with energy less than the potential barrier. 
   The number of trapped modes increases with the depth of the potential well, and the damping rate decreases. 
	\end{enumerate}
For more details on quasinormal modes see \sam{Appropriate reference needed.}

>>>>

The $w$-modes (quasinormal modes) may be divided into three branches:
	\begin{enumerate}
   \item Curvature modes, the standard $w$-modes extant for all relativistic stars. The less compact the star the more rapid the damping (Im$\{\omega\}$ increases with $R/M$). \sam{Anything else to say on curvature modes?}
   \item Interface modes ($\omega_{\text{II}}$-modes \cite{Leins:1993zz}), characterised by very rapid damping (i.e.~large negative imaginary part of $\omega_{\ell n}$). This branch of modes is somewhat similar to modes for acoustic waves scattered of a hard sphere. 
   \item Trapped modes \cite{Chandrasekhar449}: These modes exist for UCOs with $R/M < 3$, because the effective radial potential has a local minimum inside the star, and local maximum near the photon sphere $r=3M$. %The trapped modes are essentially the first few curvature modes with energy less than the potential barrier. 
   The number of trapped modes increases with the depth of the potential well, and the damping rate decreases. 
	\end{enumerate}

For more details on quasinormal modes see \sam{Appropriate reference needed.}

As far as we know, the only study into Regge pole spectra for relativistic stellar models was done by Chandrasekhar and Ferrari in 1991 \cite{ChandrasekharIV:1992ey}. They used Regge pole theory to calculate the flow of gravitational energy through a star.
